\appendix
\chapter{Cost of System}
\section{Introduction}
This appendix is committed to giving an overview of the economic requirements that this project presents.
\section{Physical requirements}
The only physical device needed for the development of the project is composed of a computer capable of handling the~\ac{ml} tasks and the deployment of the system. Since the requirements are not demanding there are many other possibilities than the one given in this appendix.\\
The technical characteristics capable of providing enough computational power for the needs presented in this project could be:
\begin{itemize}
	\item \textit{RAM}: 8 GigaByte
	\item \textit{Hard Drive Disk}: 500 GigaByte
	\item \textit{Processor}: Intel Core I7 with 4 cores
\end{itemize}
Considering the market of today and fulfilling the technical characteristics explained above, a computer of \euro{800} would be eligible.
\section{Human resources}
This section will explain the cost of having a programmer to develop the system and maintain it.\\
Considering that this project is made out of twelve ECTS and each ECTS accounts for 27 hours, the total amount of time invested in this project are at least 324 hours. Considering the average salary in Madrid (\euro{$8.12$}/hour), the project would cost around \euro{2630}.\\
Moreover, a person dedicated to the maintenance should also be considered. To that end, someone with knowledge about~\ac{ml} and~\ac{nlp}, like a Telecommunication Engineer, could be hired. In that case, a salary of~\euro{24000} could suffice.
\section{License}
This project has been done without any private license. Therefore, there is no need to spend money on a software license. This is the main benefit of using open source software. 