\begin{thebibliography}{10}

\bibitem{mexic}
Hacia la detección de ironía en textos cortos.
\newblock http://ru.ffyl.unam.mx/bitstream/handle/10391/4787/VII_CoLiCo_G_Jasso_Mesa_3_2015.pdf?sequence=2&isAllowed=y

\bibitem{luigi}
Luigi documentation.
\newblock https://media.readthedocs.org/pdf/luigi/latest/luigi.pdf.

\bibitem{sefarad}
Sefarad architecture.
\newblock https://sefarad.readthedocs.io/en/latest/sefarad.html.

\bibitem{pipeline}
Spark dataframes and ml pipelines.
\newblock https://www.slideshare.net/databricks/dataframes-and-pipelines.

\bibitem{senpy}
What is senpy?
\newblock https://senpy.readthedocs.io/en/latest/senpy.html.

\bibitem{elastic1}
Abhishek Andhavarapu.
\newblock {\em Learning Elasticsearch}.
\newblock Packt Publishing, 2017.

\bibitem{oaraque}
Oscar Araque.
\newblock {D}esign and {I}mplementation of an {E}vent {R}ules {W}eb {E}ditor.
\newblock Trabajo fin de grado, Universidad Polit{\'e}cnica de Madrid, ETSI
  Telecomunicaci{\'o}n, July 2014.

\bibitem{bird2009natural}
Steven Bird, Ewan Klein, and Edward Loper.
\newblock {\em Natural language processing with Python: analyzing text with the
  natural language toolkit}.
\newblock " O'Reilly Media, Inc.", 2009.

\bibitem{knn1}
Giuseppe Bonaccorso.
\newblock {\em Machine Learning Algorithms}.
\newblock "Packt Publishing", 2017.

\bibitem{countvect1}
Giuseppe Bonaccorso.
\newblock {\em Machine Learning Algorithms - Second Edition}.
\newblock "Packt Publishing", 2018.

\bibitem{lr1}
Andrew Bruce;~Peter Bruce.
\newblock {\em Practical Statistics for Data Scientists}.
\newblock "O'Reilly Media, Inc", 2017.

\bibitem{mltypes}
Giuseppe Ciaburro.
\newblock {\em MATLAB for Machine Learning}.
\newblock Packt Publishing, 2017.

\bibitem{elastic2}
Bharvi Dixit.
\newblock {\em Elasticsearch Essentials}.
\newblock Packt Publishing, 2016.

\bibitem{joshi2017automatic}
Aditya Joshi, Pushpak Bhattacharyya, and Mark~J Carman.
\newblock Automatic sarcasm detection: A survey.
\newblock {\em ACM Computing Surveys (CSUR)}, 50(5):73, 2017.

\bibitem{pipeline1}
Russell Jurney.
\newblock {\em Agile Data Science 2.0, 1st Edition}.
\newblock "O'Reilly Media, Inc", 2017.

\bibitem{khodak2017large}
Mikhail Khodak, Nikunj Saunshi, and Kiran Vodrahalli.
\newblock A large self-annotated corpus for sarcasm.
\newblock {\em arXiv preprint arXiv:1704.05579}, 2017.

\bibitem{nltk}
Nitin Hardeniya; Jacob Perkins; Deepti Chopra; Nisheeth Joshi;~Iti Mathur.
\newblock {\em Natural Language Processing: Python and NLTK}.
\newblock " Packt Publishing", 2016.

\bibitem{pos}
Benjamin Bengfort; Rebecca Bilbro;~Tony Ojedar.
\newblock {\em Applied Text Analysis with Python}.
\newblock " O'Reilly Media, Inc", 2018.

\bibitem{ptavcek2014sarcasm}
Tom{\'a}{\v{s}} Pt{\'a}{\v{c}}ek, Ivan Habernal, and Jun Hong.
\newblock Sarcasm detection on czech and english twitter.
\newblock In {\em Proceedings of COLING 2014, the 25th International Conference
  on Computational Linguistics: Technical Papers}, pages 213--223, 2014.

\bibitem{jfernando}
J.~Fernando S{\'a}nchez-Rada.
\newblock {D}esign and {I}mplementation of an {A}gent {A}rchitecture {B}ased on
  {W}eb {H}ooks.
\newblock Master's thesis, ETSIT-UPM, 2012.

\bibitem{tfidf1}
Sinan Ozdemir;~Divya Susarla.
\newblock {\em eature Engineering Made Easy}.
\newblock "Packt Publishing", 2018.

\end{thebibliography}
